---
title: "Assignment 2-1: Data cleaning and visualization for Question 2.1"
author: "Your Name"
date: "Today's date"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Due Sunday, February 23 @ midnight through Github**

Create a data display with the NYC HANES data to answer 

**Question 2.1: What factors measured in the NYC HANES survey are associated with having hypertension?**

You will want to think about what variables will be important to look at for examining the risk of hypertension, select these variables from the NYC HANES data set, recode and clean them, and then make some visualizations to examine the relationships among these variables. 

You should complete this assignment in this .Rmd file.  Any text you want to include should be written outside of the code chunks.  Any code must be written inside of the code chunks.

When you want to test and run your whole assignment, you can click the "Knit" button to create an HTML document with your work.

All code to read in and clean the data, and create your data display must be included in this document for it to knit properly.  That is, this document is a stand-alone document that shows all of the data analysis steps starting with the raw data.  It's helpful to periodically knit your document as you work to be sure you've included all the necessary code.

**Do the following things: **

1. Read in the NYC HANES data set and store it into an object called `dat`.  (Note, in this project the data is in a folder called `data` in the main project directory.)
```{r}
library(haven)
dat <- read_sas('data/d.sas7bdat')
dim(dat)

```

2. You will want to select some subset of variables from this data set. To know which ones you want, you can refer to the materials from class and the [Variable Codebook](https://med.nyu.edu/departments-institutes/population-health/divisions-sections-centers/epidemiology/sites/default/files/nyc-hanes-datasets-and-resources-public-dataset-codebook.pdf){target="_blank"}. You should aim to choose 8 to 10 variables that you think may be associated with hypertension. You do not need to create visualizations for all of them for this assignment, but you will eventually be interested in trying different combinations of variables when modeling hypertension as an outcome. 

Recode these variables, as we did in the class notes. Be sure to think about missing values and how you want to handle them, as well as the ordering of factor levels. Look at some summary of the resulting data set, for example using `summary` or `count`. If you see any unusual results like an unusual number of missing observations, you may want to double check your recoding against the codebook.
```{r}
### put recoding data here
### you can use comments like this to describe what you are doing

```

3. Include the code needed to make your data display here.  While working on your assignment, you might try lots of different things.  Please only include the code for the final display that you are submitting for your assignment below (delete the other things you have tried). Feel free to play around with creating a display with multiple panels, as shown in class, if you are interested.
```{r}
### put code to create data display here

```

4. Write a couple of sentences interpreting your display in context of the question of interest:

Write your text here.

5. When you have a final data display read to go, take a screenshot or download your display and post on Piazza under the Assignment 2-1 Results thread.  You are welcome to post your screenshot anonymously to your classmates.

6. When you are ready to submit your assignment, do ALL of the following:

* First, knit your .Rmd file to see if it will compile.  If it doesn't knit, you can still follow the steps below to submit your assignment, but please try to resolve the knitting issues before you submit.  You can reach out to us at phbiostats@jhu.edu for help!
* Next you need to **commit** the changes you've made to the document.  Click the colorful Git button at the top of the RStudio window and select "Commit" from the menu.
* In the window that opens, **stage** your changes by clicking the check boxes next to the `Asst2-1.Rmd` file.
* In the "Commit message" box, type a short description of what changes you've made, something like: `Completed assignment`
* Click the "Commit" button on the bottom right.
* You'll see a window that will tell you about the changes that you've made.  Click "Close" to close the window.  You've successfully committed! You can close this commit window now.
* After committing, you must **push** your changes to the repository on Github.  Do this by clicking the colorful Git button again and select "Push Branch".  
* Again, you'll see a window open that tells you your changes have been pushed!
* If you want, you can look at your repository on [Github.com](https://github.com/) and should be able to see your changes there!  
* You've successfully submitted your assignment :)

